---
title: "Challenge 3"
author: 'Stephen Wessel'
format: html
editor: visual
---

## Import Libraries

```{r}
#| warning: false
#| message: false
library(tidyverse)
```

## Load Data

```{r}
hip_hop <- read_csv(here :: here('Week 3','hiphop.csv'),col_type=cols())
```

## Restructure Data

```{r}
hip_hop <- hip_hop |> 
  mutate(ethnic_w = ifelse(ethnic=='white','white','non-white')
  ) |> 
  distinct(subj,.keep_all = TRUE) |> 
  subset(select = c(subj, sex, age, ethnic, intl, vocal, classical, folk,
                    rock, country, pop, alternative, hiphop, unclassifiable,
                    ethnic_w)) 

```

## Challenge 2

```{r}
hip_hop |> 
  group_by(sex) |> 
  summarise(mean_intl = mean(intl),
            mean_vocal = mean(vocal),
            mean_classical = mean(classical),
            mean_folk = mean(folk),
            mean_rock = mean(rock),
            mean_country = mean(pop),
            mean_alternative = mean(alternative),
            mean_hiphop = mean(hiphop),
            mean_unclassifiable = mean(unclassifiable))
```

It appears that male subjects reported to like on average 3.059 rock and roll artists where female subjects reported only liking on average 1.932 rock and roll artists.

```{r}
hip_hop |> 
  group_by(ethnic_w) |> 
  summarise(mean_intl = mean(intl),
            mean_vocal = mean(vocal),
            mean_classical = mean(classical),
            mean_folk = mean(folk),
            mean_rock = mean(rock),
            mean_country = mean(pop),
            mean_alternative = mean(alternative),
            mean_hiphop = mean(hiphop),
            mean_unclassifiable = mean(unclassifiable))
```

It again appears that white subjects reported to like on average 2.570 rock and roll artists where non-white subjects reported only liking on average 1.061 rock and roll artists.

## Study Design Technique

1.  First it seems like the individuals conducting the experiment are assuming that black people will automatically know all the AAE vocabulary which I think is assuming too much.
2.  Secondly, the experimenter was more concerned with finding out information on hip-hop knowledge as the main source of variation for AAE vocabulary knowledge.
