---
title: "Data Import Practice"
author 'Stephen Wessel'
format: html
editor: visual
---

## Library Imports

```{r}
#| warning: false
#| message: false
library(tidyverse)
library(readxl)
```

## Step 1: Read in the dataset `ages.csv`.

```{r}
# Code to read in the ages.csv data goes here! 
ages = read_csv(here :: here('Ages_Data','Ages_Data', 'ages.csv'))

```

## Step 2: Read in the dataset `ages_tab.txt`

```{r}
# Code to read in the ages_tab.txt data goes here! 

#| warning: false
#| message: false
# Code to read in the ages.csv data goes here! 
ages = read_tsv(here :: here('Ages_Data','Ages_Data', 'ages_tab.txt'))
```

## Step 3: Read in the dataset `ages_mystery.txt`

```{r}
# Code to read in the ages_mystery.txt data goes here! 


#| warning: false
#| message: false
# Code to read in the ages.csv data goes here! 
ages = read_delim(here :: here('Ages_Data','Ages_Data', 'ages_mystery.txt'),
                delim = '|')
```

## Step 4: Read in the dataset `ages.xlsx`

```{r}
# Code to read in the ages.xlsx data goes here! 
ages = read_excel(here :: here('Ages_Data','Ages_Data', 'ages.xlsx'))

```

## Step 5: Both `read.csv` and `read.table` have an optional argument called `stringsAsFactors`. Figure out what this does.

## Step 6: Find a way to use `read_csv()` to read `ages.csv` with the variable "Name" as a factor and "Age" as a character.

```{r}
# Code to read in the ages.csv with "Name" as a factor and "Age" as a character goes here! 


```

------------------------------------------------------------------------
