---
title: "Challenge 4"
format: html
editor: visual
---

## Import Libraries

```{r}
#| warning: false
#| message: false
library(tidyverse)
```

## Read in Data

Avocado contains data includes information on retail information including volume and cost on avocados from multi-outlet sources. Median_Housing_Price contains information on the median housing price for each region that I found from google.

```{r}
#| warning: false
#| message: false
region <- c('LosAngeles', 'SanDiego', 'Sacramento', 'SanFrancisco')
median_housing_price <- c(1000000, 885000, 475136, 1300000)
region_median_price <- data.frame(region, median_housing_price)

avocado <- read_csv(here :: here('Week 4','avocado.csv'),col_type=cols())
```

## 

```{r}
#| warning: false
#| message: false
region <- c('LosAngeles', 'SanDiego', 'Sacramento', 'SanFrancisco')
df_california <- data.frame(region)

avocado |> 
  semi_join(df_california) |> 
  group_by(region) |> 
  summarise(across(AveragePrice, mean)) |> 
  left_join(region_median_price) |> 
  ggplot(mapping = aes(y = AveragePrice, x = median_housing_price)) +
  geom_point()
  

```

```{r}
#| warning: false
#| message: false
avocado |> 
  semi_join(df_california) |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  group_by(region) |> 
  summarize_at(.cols = 'Number_Avocados', .funs = mean) |> 
  left_join(region_median_price) |> 
  ggplot(mapping = aes(y = Number_Avocados, x = median_housing_price)) +
  geom_point()
```

For both number of avocados sold and the mean avocado price, there does not seem to be any type of relationship to housing.
