---
title: "Lab 4"
format: html
editor: visual
---

## Import Libraries

```{r}
#| warning: false
#| message: false
library(tidyverse)
```

## Read in Data

This data includes information on retail information including volume and cost on avocados from multi-outlet sources.

```{r}
avocado <- read_csv(here :: here('Week 4','avocado.csv'),col_type=cols())
```

## Data Cleaning

Region has four different naming conventions. These include Total United States, State, City, and Region

```{r}
region <- c('GreatLakes', 'Midsouth', 'Northeast',
             'Plains', 'SouthCentral', 'Southeast',
             'West')
df_major_regions <- data.frame(region)

region <- c('California', 'SouthCarolina')
df_major_states <- data.frame(region)

region <- c('TotalUS')
df_total_us <- data.frame(region)


region_avocado <- avocado |> 
  semi_join(df_major_regions)

city_avocado <- avocado |> 
  anti_join(df_major_regions) |> 
  anti_join(df_major_states) |> 
  anti_join(df_total_us)
```

## Exercises

3.  

```{r}
type <- c('organic')

df_organic_small = data.frame(type)

region_avocado |> 
  semi_join(df_organic_small) |> 
  group_by(region) |> 
  summarize_at(.cols = '4225', .funs = sum)
```

It appears that the west region sold the most organic small hess avocados.

4\.

```{r}
avocado |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  separate(col=Date, into=c('year', 'month', 'day'), sep='-') |> 
  group_by(month) |> 
  summarize_at(.vars = 'Number_Avocados', .funs = sum)
  
```

```{r}
avocado |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  separate(col=Date, into=c('year', 'month', 'day'), sep='-') |> 
  group_by(month) |> 
  summarize(across(c('Number_Avocados'), sum))
```

February seems to have the most avocados sold than any other month.

5\.

```{r}
top_cities <- city_avocado |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  group_by(region) |> 
  summarize_at(.cols = 'Number_Avocados', .funs = sum) |> 
  arrange(desc(Number_Avocados)) |> 
  head(n = 5)

avocado |> 
  semi_join(top_cities) |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  ggplot(mapping = aes(y = Number_Avocados, x = region)) +
  geom_boxplot()
```

6\.

```{r}
region <- c('LosAngeles', 'SanDiego', 'Sacramento', 'SanFrancisco')
df_california <- data.frame(region)

avocado_california <- avocado |> 
  semi_join(df_california) 
avocado_california_difference <- avocado_california |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados')  |> 
  group_by(region, type) |> 
  summarise_at(.cols = 'AveragePrice', .funs = mean) |> 
  pivot_wider(names_from = type, values_from = AveragePrice) |> 
  mutate(difference = organic - conventional)
avocado_california_difference
```

```{r}
avocado_california_difference |> 
  ggplot(mapping = aes(x = region, y = difference)) +
  geom_bar(stat = "identity")+
  ylab('Difference between Organic and Conventional') +
  xlab('City')
```

It seems like the city with the biggest difference between conventional and organic mean price in avocados for the cities, San Diego, Los Angeles, Sacramento and San Francisco is San Francisco.

7\.

```{r}
avocado_sales_per_PLU_type_region <- avocado_california  |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  group_by(type, PLU, region) |> 
  summarise_at(.cols = 'Number_Avocados', .funs = sum) 

avocado_sales_per_region <- avocado_california  |> 
  pivot_longer(cols = `4046`:`4770`, names_to = 'PLU', values_to = 'Number_Avocados') |> 
  group_by(type, region) |> 
  summarise_at(.cols = 'Number_Avocados', .funs = sum) |> 
  rename('Total_Avocados' = 'Number_Avocados')

avocado_sales_per_PLU_type_region |> 
  left_join(avocado_sales_per_region) |> 
  mutate(PLU = recode(PLU, `4046` = 'Small', `4225` = 'Large', `4770` =  'Extra Large' )) |> 
  mutate(mean_percentage = Number_Avocados / Total_Avocados) |> 
  ggplot(aes(x = region, y=mean_percentage, fill=PLU)) + 
  facet_wrap(~type) +
  geom_col(stat="identity") +
  scale_x_discrete(guide = guide_axis(n.dodge=2)) +
  xlab('Region of CA') +
  ylab('Proportion of Mean Avocados Sold')
```
